%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{ Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
 
  \cventry
    {Chairperson Computer Science Department} % Job title
    {Harare Institute of Technology} % Organization
    {Harare, Zimbabwe} % Location
    {July 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing the day to day operations of the Department.}
        \item {Creating Strategic plans to align the department to the Institution’s mandate.}
        \item {Representing the Department and Institute at various meetings and conferences.}
        \item {Curriculum review for Bachelor of Technology programmes in the School of Information Sciences.}
        \item {Crafting of Regulations for Bachelor of Technology and Master of Technology Programs.}
        \item {Technical Consultancy and spearheading drives towards industrial partnerships.}
        \item {Peer review coordination and assessment of Department staff members.}
        \item {Staff recruitment and interviews}
        \item {Duty delagation and supervision of staff members.}
        \item {Enrolment and selection of new students.}
        \item {Budgeting and Planning for the department.}
        \item {Producing various reports for senior management.}
        \item {Convening of Departmental Board meetings}
        \item {Attending of Institute Academic and Senate Board Meetings}
        \item {Representing the Department and Institute at various meetings and conferences.}
        \item {Providing counselling and mentorship to students.}
        \item {Conducting workshops, research and training.}
      \end{cvitems}
    }



 %-------------------------------------------------------------------------------
 \cventry
 {Lecturer} % Job title
 {Harare Institute of Technology} % Organization
 {Harare, Zimbabwe} % Location
 {June 2016 -  Present} % Date(s)
 {
   \begin{cvitems} % Description(s) of tasks/responsibilities
     \item {Instructor for Introduction to C Programming, Object Orientented Programming, Technical Communication Skills, Web Programming and Introduction to Computer Science.}
     \item {Preparation of laboratory learning material.}
     \item {Conducting programming laboratory sessions.}
     \item {Marking assignments, laboratory work and examinations.}
     \item {Assessment of students on internship.}
     \item {Conducting academic research work.}
     \item {Supervision of Part II and Part IV design and research projects.}
   \end{cvitems}
 }   

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Director} % Job title
    {Gisul Solutions Pvt Ltd} % Organization
    {Harare,Zimbabwe} % Location
    {1 January 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementation of a custom linux gateway at Marlborough High School to filter content available to students at the school. This was done to reduce load on bandwidth and also only allow students to acccess educational websites and protect them from the dangers of an unfiltered internet.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching \& Research Assistant} % Job title
    {Harare Institute of Technology} % Organization
    {Harare, Zimbabwe} % Location
    {August 2013 - July 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisting lecturers by conducting tutorials and marking of assignments.}
        \item {Conducting research and finding new ways to boost and improve the institute Curriculum using experience gained in South Korea.}
        \item {Member of the department time table and resource mobilisation committees.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
\cventry
{Front End Web Developer - Intern} % Job title
{Webdev Zimbabwe} % Organization
{Harare, Zimbabwe} % Location
{August 2011 - May 2012} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Liasing with the project manager about user specifications and requirements.}   
    \item {Liasing with the client about their user specifications and requirements.}
    \item {Converting the graphic desiners work into code using HTML and CSS.}
    \item {Designing and coding custom components using Javascript.}
    \item {Providing the project manager the costing sheet based on specifications and time required.}
    \item {Deployment of web applications from development server to live server.}
    \item {Training of end users about how to use the system after deployement.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
